Analytical Predictions of Explanet Obliquities Generated by Planet-Disk Interactions

### 2020-01-23 writeups/Su_weak_tides.tex
put a few prelim plots into outline

\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
Obliquities Generated by Planet-Disk Interactions}
\author[Y. Su and D. Lai]{
Yubo Su$^1$,
Dong Lai$^1$
\\
$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
Astronomy, Cornell University, Ithaca, NY 14853, USA
}

@@

The phase portrait for these EOM in $\p{s, \theta}$ space is shown in
Fig.~flow-diagram.

% \label{fig:flow-diagram}

TODO overplot CS1, CS2 for two values of $s_c$. TODO show on plot the location
where tides are so strong that CS2 ecomes unstable (is the only
$\epsilon$-dependent result of the paper).

@@

Generally, these EOM have equilibria at the points that are both a CS and
satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~flow-diagram, these are the
intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
clear that the locations of these equilibria depend on the value of $s_c$. Call
these generalized equilibria \emph{tidal Cassini States} (tCS), and number them
tCS1 and tCS2 depending on whether they are CS1 or CS2 states.

@@

As a result of \autoref{ss:tidal_eqs}, the tCS are the only possible final
outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
generally cannot be fixed by any formation mechanism) in histograms:

% Three primary regimes: $s_c \ll 1$ (CS2 rare), $\simeq 1$ (CS2 is substantial
% and probable), $\gg 1$ (CS2 = I, uninteresting)

The governing mechanism for these probabilities is probabilistic separatrix
crossing, which is covered in Appendix~\ref{app:probs}. The calculation is
difficult analytically, but can be performed semi-analytically (describe
procedure here, calculate $\eta_{\star}$ numerically etc.). The agreement of
this curve with the histograms is examined for the same three $s_c$ values
below:

@@

Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
calculate the probabilities of going to either tCS as a function of $s_c$. This
is shown below:

>>>>

\title[Analytical Exoplanet Obliquities]{Analytical Predictions of Explanet
Obliquities Generated by Planet-Disk Interactions}
\author[Y. Su and D. Lai]{
Yubo Su$^1$,
Dong Lai$^{1,2}$
\\
$^1$ Cornell Center for Astrophysics and Planetary Science, Department of
Astronomy, Cornell University, Ithaca, NY 14853, USA
\\
$^2$ Tsung-Dao Lee Institute, 800 Dongchuan Road, Shanghai, 200240, China
}

@@

The phase portrait for these EOM in $\p{s, \theta}$ space is shown in
Fig.~\ref{fig:quiver}.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/2quiver0_2.png}
    \caption{Phase portrait.}\label{fig:quiver}
\end{figure}

TODO overplot CS1, CS2 for \emph{two} values of $s_c$. TODO show on plot the location
where tides are so strong that CS2 ecomes unstable (is the only
$\epsilon$-dependent result of the paper).

@@

Generally, these EOM have equilibria at the points that are both a CS and
satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~\ref{fig:quiver}, these are the
intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
clear that the locations of these equilibria depend on the value of $s_c$. Call
these generalized equilibria \emph{tidal Cassini States} (tCS), and number them
tCS1 and tCS2 depending on whether they are CS1 or CS2 states.

@@

As a result of \autoref{ss:tidal_eqs}, the tCS are the only possible final
outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
generally cannot be fixed by any formation mechanism) in histograms. This gives
histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
    \caption{$s_c = 0.06$. Note that it is difficult to reach
    tCS2.}\label{fig:Hhists_0_06}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
    \caption{$s_c = 0.2$. Note that tCS2 is both reached with substantial
    probability and has substantial obliquity.}\label{fig:Hhists_0_20}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
    \caption{$s_c = 0.6$. Note that tCS2 becomes attracting over tCS1, but will
    have obliquity $\approx I$ and is uninteresting.}\label{fig:Hhists_0_70}
\end{figure}

The governing mechanism for these probabilities is probabilistic separatrix
crossing, which is covered in Appendix~\ref{app:probs}. The calculation is
difficult analytically, but can be performed semi-analytically (describe
procedure here, calculate $\eta_{\star}$ numerically etc.). The agreement of
this curve with the histograms is examined for the same three $s_c$ values
in Figs.~\ref{fig:pc_fits_0_06,fig:pc_fits_0_20,fig:pc_fits_0_70}.
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_06_5.png}
    \caption{$s_c = 0.06$ fit to histogram.}\label{fig:pc_fits_0_06}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_20_5.png}
    \caption{$s_c = 0.20$ fit to histogram.}\label{fig:pc_fits_0_20}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5pc_fits0_70_5.png}
    \caption{$s_c = 0.70$ fit to histogram.}\label{fig:pc_fits_0_70}
\end{figure}

@@

Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
calculate the probabilities of going to either tCS as a function of $s_c$. This
is shown below for $I = 5^\circ$
\begin{figure}[t]
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
    \caption{Total probabilities of ending up in either tCS and their ossicated
    final obliquities.}\label{fig:probs}
\end{figure}
